---
title: "Case Study"
output: html_document
---

Today we're studying a case.

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(leaflet)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Get Data

```{r}
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb =
  nyc_airbnb %>% 
  rename(borough = neighbourhood_group) %>% 
  mutate(stars = review_scores_location / 2)
```



## Brainstorm questions

* what variables are relevant to higher review / scores?

```{r}

```

* what are the popular places to rent an Airbnb?

```{r}
nyc_airbnb %>%
  group_by(neighbourhood, borough) %>%
  distinct() %>%
  summarize(n_obs = n()) %>%
  ungroup() %>% 
  group_by(borough) %>% 
  mutate(rank = min_rank(desc(n_obs))) %>% 
  filter(rank < 5) %>% 
  arrange(borough, desc(n_obs))

nyc_airbnb %>% 
  ggplot(aes(x = borough, fill = borough)) +
  geom_bar() +
  labs(
    x = "Neighbourhood Group",
    y = "Number of Airbnbs",
    title = "Distribution of Airbnbs in New York City by Borough",
    ) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
    )

nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  ggplot(aes(x = neighbourhood)) +
  geom_bar() +
  labs(
    x = "Neighbourhood",
    y = "Number of Airbnbs",
    title = "Distribution of Airbnbs in Manhattan, New York City",
    ) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank()
    )
```

* what proportion of hosts / locations are private rooms vs entire apartments?

```{r}

```

* what makes an airbnb more expensive?

Let's look at the price ..

```{r}
nyc_airbnb %>% 
  group_by(borough, room_type) %>% 
  summarise(
    mean_price = mean(price, na.rm = TRUE)
  ) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

Look at price distributions

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price < 1000) %>% 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ room_type)
```

Price vs rating ?

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  facet_grid(. ~ room_type)
```

Somewhat fancy boxplot!

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarise(
    mean_price = mean(price, na.rm = TRUE)
  ) %>% 
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan",
         room_type == "Entire home/apt") %>% 
  filter(price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()

nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  filter(price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() +
  facet_grid(. ~ room_type)
```

Price vs location

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan",
         room_type == "Entire home/apt") %>% 
  filter(price <= 1000) %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .5)
```


Let's make a map by `leaflet`

```{r}
pal = colorNumeric("viridis", domain = c(0, 1000))

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         room_type == "Entire home/apt") %>% 
  filter(price <= 1000) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~ lat, ~ long, radius = .5, color = ~ pal(price))
```

